The Hydrogen Epoch of Reionization Array Dish I: Beam Pattern Measurements and Science Implications

### 2016-01-23 DishBeamMeasurements/paper/DishBeamMeasurementsPaper_rev2.tex
rev2

\affil{\altaffilmark{1}MIT Kavli Institute, Massachusetts Institute of Technology, Cambridge, MA, 02139 USA}
\affil{\altaffiltext{2}Dept. of Electrical and Computer Engineering, University of Virginia, Charlottesville, VA, 22904}
\affil{\altaffiltext{3}National Radio Astronomy Obs., Charlottesville, VA}
\affil{\altaffilmark{4}Dept. of Astronomy, University of California, Berkeley, CA, USA}
\affil{\altaffilmark{5}Arizona State University, School of Earth and Space Exploration, Tempe, AZ 85287, USA}
\affil{\altaffilmark{6}Dept. of Physics and Astronomy, University of Pennsylvania, Philadelphia, PA}

@@

The fact that sources acquire frequency dependence based on with their position on the sky 
tells us already that the primary beam strongly affects the aggregate frequency dependence 
of the foregrounds. The high delay regions of the sky lie near the horizon while low delay 
regions lie closer to zenith and also perpendicular to the baseline vector. \citet{nithya15} 
simulate the foreground contamination seen with a dipole beam, a phased array, and a Airy dish,
and find that the latter suffers the least foreground leakage into
 $k_\parallel>0$ modes due to its narrow main lobe and minimal sidelobe 
levels. To be sure, all are subject to the same geometric limits on foreground frequency-
dependence limiting foreground bounding foreground emission within the wedge, but the emission from high delay is better suppressed using the 
Airy dish leaving much of the wedge effectively empty.

@@

The HERA element is a 14\,m diameter parabolic dish ($f/D\approx0.32$) with a dual-polarized dipole feed (Fig. \ref{fig:feedphoto}) suspended at prime focus. The dish surface is formed by sheets of wire attached to PVC tubes attached to supports at the edge of the dish and to a hub at the base. The feed is suspended with cables attached to three telephone poles around the dish. For feed maintenance purposes, a door is engineered into the dish surface on one mesh panel. The feed stands 17\,in off a mesh back plane surrounded by a XX\,in deep cylinder. The nominal dish focus is at 4.5\,m from the dish surface to the feed back plane, though numerical models suggest the focus is closer to 5.3\,m. The feed is designed to make the beams for both polarizations more similar to each other, and also to taper the dipole beam towards the edge of the dish to mitigate dish-dish coupling.

@@

\begin{figure}[h]
\includegraphics[width=3.4in]{feed.jpg}
\caption{Prototype HERA feed set up outside the dish for preliminary characterization. This feed revision consists of a dual-polarized sleeved dipole offset 17\,in from a XX\,in diameter back plane, surrounded by a XX\,in deep cylindrical skirt.}
\label{fig:feedphoto}
\end{figure}

@@

We turn in this section to the effects of the beam power pattern on the apparent frequency dependence of the foregrounds. Thyagarajan et al., (submitted) discuss the apparent frequency dependence of foregrounds in more detail as well as methods to mitigate it such as delay space CLEANing. We focus on this section on the uncertainties in these foreground power spectrum simulations due to beam modeling uncertainties, but we must first discuss these foreground simulations themselves and their dependence on observing conditions.

We simulate foreground power spectra using different primary beam models at various local sidereal times (LSTs). Given that our measured dish power patterns agree well with both numerical models (HFSS and CST) in the main lobe but deviate in the sidelobes, and that these models make somewhat different assumptions about the dish surface, we take them as a representative pair of possible dish models. We use a feed height of 5\,m, a compromise between larger collecting area and smaller risk of coupling to adjacent dishes. We also include the Airy pattern for comparison as \citet{nithya15}. Beam models with weaker response near the horizon (such as the Airy pattern) downweight sources in this direction of high apparent frequency dependence. This reduces the magnitude of emission near the edge of the EOR window, reducing the risk it leaks inside. We use the per-baseline approach of \citet{parsons12a,parsons12b}, simulating visibilities measured by specific baselines as a function of frequency, then computing the Fourier transform over frequency (delay transform) and normalizing the result into a cosmological power spectrum following \citet{nithya15}.

>>>>

\affil{\altaffilmark{1}MIT Kavli Institute, Massachusetts Institute of Technology, Cambridge, MA, 02139 USA}
\affil{\altaffilmark{2}Dept. of Electrical and Computer Engineering, University of Virginia, Charlottesville, VA 22904}
\affil{\altaffilmark{3}National Radio Astronomy Obs., Charlottesville, VA}
\affil{\altaffilmark{4}Dept. of Astronomy, University of California, Berkeley, CA, USA}
\affil{\altaffilmark{5}Arizona State University, School of Earth and Space Exploration, Tempe, AZ 85287, USA}
\affil{\altaffilmark{6}Dept. of Physics and Astronomy, University of Pennsylvania, Philadelphia, PA}

@@

The fact that sources acquire frequency dependence based on with their position on the sky 
tells us already that the primary beam strongly affects the aggregate frequency dependence 
of the foregrounds. The high delay regions of the sky lie near the horizon while low delay 
regions lie closer to zenith and also perpendicular to the baseline vector. \citet{nithya15} 
simulate the foreground contamination seen with a dipole beam, a phased array, and a Airy pattern,
and find that the latter suffers the least foreground leakage into
 $k_\parallel>0$ modes due to its narrow main lobe and minimal sidelobe 
levels. To be sure, all are subject to the same geometric limits on foreground frequency-
dependence limiting foreground bounding foreground emission within the wedge, but the emission from high delay is better suppressed using the 
Airy pattern leaving much of the wedge effectively empty.

@@

The HERA element is a 14\,m diameter parabolic dish ($f/D\approx0.32$) with a dual-polarized dipole feed (Fig. \ref{fig:feedphoto}) suspended at prime focus. The dish surface is formed by sheets of wire attached to PVC tubes attached to supports at the edge of the dish and to a hub at the base. The feed is suspended with cables attached to three telephone poles around the dish. For feed maintenance purposes, a door is engineered into the dish surface on one mesh panel. The dipole stands 17\,in below a 78\,in diameter circular mesh back plane surrounded by a 30\,in deep cylinder. The cylinder is offset 0.5\,in from the back plane. The feed is designed to make the beams for both polarizations more similar to each other, and also to taper the dipole beam towards the edge of the dish to mitigate dish-dish coupling.  The nominal dish focus is at 4.5\,m from the dish surface, though numerical dish models including the feed predict the focus is closer to 5.3\,m.

@@

\begin{figure}[h]
\includegraphics[width=3.4in]{feed.jpg}
\caption{Prototype HERA feed set up outside the dish for preliminary characterization. This feed revision consists of a dual-polarized sleeved dipole offset 17\,in from a 78\,in diameter back plane, surrounded by a 30\,in deep cylindrical skirt.}
\label{fig:feedphoto}
\end{figure}

@@

We turn in this section to the effects of the beam power pattern on the apparent frequency dependence of the foregrounds. Thyagarajan et al., (submitted) discuss the apparent frequency dependence of foregrounds in more detail as well as methods to mitigate it such as delay space CLEANing. We focus in this section on the uncertainties in these foreground power spectrum simulations due to beam modeling uncertainties, but we must first discuss these foreground simulations themselves and their dependence on observing conditions.

We simulate foreground power spectra using different primary beam models at various local sidereal times (LSTs). We use frequency-independent model beams (evaluated at 137\,MHz) to isolate the interferometric foreground frequency dependence. The added frequency dependence of the changing overall gain and beam shape versus frequency is addressed by the other papers in this series. Given that our measured dish power patterns agree well with both numerical models (HFSS and CST) in the main lobe but deviate in the sidelobes, and that these models make somewhat different assumptions about the dish surface, we take them as a representative pair of possible dish models. We use a feed height of 5\,m, a compromise between collecting area and risk of coupling to adjacent dishes. We also include the Airy pattern for comparison as in \citet{nithya15}. Beam models with weaker response near the horizon (such as the Airy pattern) downweight sources in this direction of high apparent frequency dependence. This reduces the magnitude of emission near the edge of the EOR window, reducing the risk it leaks inside. We use the per-baseline approach of \citet{parsons12a,parsons12b}, simulating visibilities measured by specific baselines as a function of frequency, then computing the Fourier transform over frequency (delay transform) and normalizing the result into a cosmological power spectrum following \citet{nithya15}.
